```{r}
library('rethinking')
data(Howell1)
d = Howell1
d2= d[d$age>=18, ]
```
```{r}
precis(d)
```
Plot the mu prior

```{r}
curve(dnorm(x, 178, 20), from =100, to =250)
```

Plot the sigma prior
```{r}
curve(dunif(x, 0, 50), from=-10, to=60)
```

```{r}
x_bar = mean(d2$weight)

m4.3 = quap(alist(
  height ~ dnorm(mu, sigma),
  mu <- a + b * (weight - x_bar),
  a ~ dnorm(178, 20),
  b ~ dlnorm(0, 1),
  sigma ~ dunif(0, 50)
),
data = d2)
```
```{r}
summary(m4.3)
```
```{r}
round(vcov(m4.3), 3)
```

```{r}
pairs(m4.3)
```
```{r}
plot(height~weight, data=d2, col=rangi2)
post = extract.samples(m4.3)
a_map = mean(post$a)
b_map = mean(post$b)
curve(a_map+b_map*(x-x_bar), add=TRUE)

```

```{r}
mu=link(m4.3)
```
```{r}
weight.seq = seq(25, 70, .1)
sim.height=sim(m4.3, data=list(weight=weight.seq))
str(sim.height)
```

```{r}
height.PI = apply(sim.height, 2, PI, prob=0.89)
```

```{r}
post = extract.samples(m4.3)
mu.link = function(weight) post$a+post$b*(weight-x_bar)
mu = sapply(weight.seq, mu.link)
mu.mean = apply(mu, 2, mean)
mu.HPDI = apply(mu, 2, HPDI, prob=0.89)
plot(height~weight , d2, col=col.alpha(rangi2, 0.5))
lines(weight.seq, mu.mean)
shade(mu.HPDI, weight.seq)
shade(height.PI, weight.seq)

```

## 4E1

The first line is the likelihood

## 4E2

There are two parameters in the posterior

## 4E3

$Pr(\mu, \sigma|y) = \frac{\prod_i Normal(y_i|\mu, \sigma)Normal(\mu|0, 10)Exponential(\sigma|1)}{\int \int \prod_i Normal(y_i|\mu, \sigma)Normal(\mu|0, 10)Exponential(\sigma|1) d\mu d\sigma}$

## 4E4

The 2nd line

## 4E5

There are three parameters, alpha, beta and sigma.

## 4M1

```{r}
n_samples = 10000
mu_samples = rnorm(n_samples, mean = 0, sd = 10)
sigma_samples = rexp(n_samples, rate = 1)
y_samples = rnorm(n_samples, mean = mu_samples, sd = sigma_samples)
dens(y_samples)
```


## 4M2

```{r}
quap_f = alist(
  h ~ dnorm(mu, sigma),
  mu ~ dnorm(0, 10),
  sigma ~ dexp(1)
)
```

## 4M3

$$
\begin{align}
& y_i = Normal(\mu, \sigma) \\
& \mu = \alpha + \beta x_i \\
& \alpha = Normal(0, 10) \\
& \beta = Uniform(0,1) \\
& \sigma = Exponential(1)
& \end{align}
$$

## 4M4

$$
\begin{align}
& h_i = Normal(\mu, \sigma) \\
&\mu = alpha + \beta y_i \\
&\alpha = Gamma(980, 1/7) \text{ Where the parameters are shape and theta respectively} \\
&\beta = Gamma(4, 1.5) \\
&\sigma = Exponential(1)
\end{align}
$$
## 4M5

No. 

## 4M6

I will chose a distribution for sigma that doesn't allow for values greater then 64.

## 4H1

```{r}
library(rethinking)
data(Howell1)
d = Howell1
d2 = d[d$age >= 18 , ]
# define the average weight
xbar = mean(d2$weight)
m4.3 = quap(alist(
  height ~ dnorm(mu , sigma) ,
  mu <- a + b * (weight - xbar) ,
  a ~ dnorm(178 , 20) ,
  b ~ dlnorm(0 , 1) ,
  sigma ~ dunif(0 , 50)
) ,
data = d2)
```

```{r}
post_samples = extract.samples(m4.3)
head(post_samples)
```
```{r}
precis(m4.3)
```
```{r}
weight = 46.95
mu_preds = post_samples$a + post_samples$b*(weight-xbar)
dens(mu_preds)
```

```{r}
PI( mu_preds , prob=0.89 )
```
```{r}
height_preds = rnorm(10000, mean=mu_preds, sd= post_samples$sigma)
dens(height_preds)
```
```{r}
precis(mu_preds)
precis(height_preds)
```
```{r}
PI( height_preds , prob=0.89 )
```


```{r}
# weight.seq = seq( from=25 , to=70 , by=1 )
weight.seq= c(32.59, 43.72, 46.95, 54.63, 64.78)
mu = link(m4.3, data=data.frame(weight=weight.seq))
```

```{r}
# plot( height ~ weight , d2, type='n')
plot(x=NULL, y=NULL, xlim=c(floor(min(weight.seq)), ceiling(max(weight.seq))), ylim=c(floor(min(mu)), ceiling(max(mu))))
for ( i in 1:100 )
  points( weight.seq , mu[i,] , pch=16 , col=col.alpha(rangi2,0.1) )
```
```{r}
mu.mean <- apply( mu , 2 , mean )
mu.PI <- apply( mu , 2 , PI , prob=0.89 )

# plot raw data
# fading out points to make line and interval more visible
plot( height ~ weight , data=d2 , col=col.alpha(rangi2,0.5) )
# plot the MAP line, aka the mean mu for each weight
lines( weight.seq , mu.mean )
# plot a shaded region for 89% PI
shade( mu.PI , weight.seq )
```
```{r}
sim.height <- sim( m4.3 , data=list(weight=weight.seq) )
height.PI <- apply( sim.height , 2 , PI , prob=0.89 )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )
```
```{r}
# plot raw data
plot( height ~ weight , d2 , col=col.alpha(rangi2,0.5) )
# draw MAP line
lines( weight.seq , mu.mean )
# draw HPDI region for line
shade( mu.HPDI , weight.seq )
# draw PI region for simulated heights
shade( height.PI , weight.seq )
```

The values required to fill in the table
```{r}
mu.mean

```

```{r}
height.PI 
```

## 4H2

```{r}
library(rethinking)
data(Howell1)
d = Howell1
d2 = d[d$age < 18 , ]
```
```{r}
precis(d2)
```
```{r}
xbar = mean(d2$weight)
m4.3b = quap(alist(
  height ~ dnorm(mu , sigma) ,
  mu <- a + b * (weight - xbar) ,
  a ~ dnorm(178 , 20) ,
  b ~ dlnorm(0 , 1) ,
  sigma ~ dunif(0 , 50)
) ,
data = d2)
```
```{r}
precis(m4.3b)
```
## a

For every 10 units of increa in weight, the predicted increas in tallness is, on average, 27.2

## b

```{r}
weight.seq = seq( from=25 , to=70 , by=1 )
sim.height <- sim( m4.3b , data=list(weight=weight.seq) )
height.PI <- apply( sim.height , 2 , PI , prob=0.89 )
```
```{r}
# plot raw data
plot( height ~ weight , d2 , col=col.alpha(rangi2,0.5) )
# draw MAP line
lines( weight.seq , mu.mean )
# draw HPDI region for line
shade( mu.PI , weight.seq )
# draw PI region for simulated heights
shade( height.PI , weight.seq )
```


