```{r}
library('rethinking')
library(tidyverse)
```


```{r}
p_grid = seq(from=0, to=1, length.out=1000)
prob_p = rep(1, 1000)
prob_data = dbinom(6, size=9, prob=p_grid)
posterior = prob_data*prob_p
posterior = posterior/sum(posterior)
set.seed(100)
n_samples = 1e4
samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
```

Check that the posterior is a possible probability mass function (note: the variable is discrete)

```{r}
sum(posterior) # Must be 1
```

```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```

```{r}
dens(samples)
```
```{r}
sum(posterior[p_grid<0.2])
sum(samples<0.2)/n_samples
```
```{r}
sum(posterior[p_grid>0.8])
#sum(samples>0.8)/n_samples
mean(samples > 0.8)
```

```{r}
sum(posterior[0.2<p_grid & p_grid<0.8])
sum(samples>0.2 & samples<0.8)/n_samples
```
```{r}
mean(between(samples, 0.2, 0.8))
```


```{r}
quantile(samples, .2)
```

```{r}
quantile(samples, .8)
```

```{r}
HPDI(samples, .66)
```

```{r}
PI(samples, .66)
```
## 3M1

Posterior distribution using grid approximation for 8 W globe tosses out of 15.

```{r}
p_grid = seq(from=0, to=1, length.out=1000)
prob_p = rep(1, 1000)
prob_data = dbinom(8, size=15, prob=p_grid)
posterior = prob_data*prob_p
posterior = posterior/sum(posterior)
```

```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```


## 3M2

```{r}
set.seed(100)
n_samples = 1e4
samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
HPDI(samples, .90)
```
```{r}
dens(samples)
```

```{r}
post_predictions = rbinom(10000, size=15, prob=samples)
sum(post_predictions == 8)/length(post_predictions)
mean(post_predictions == 8)
```

##############################################################

## 3M1

Posterior distribution using grid approximation for 8 W globe tosses out of 15.

```{r}
p_grid = seq(from=0, to=1, length.out=1000)
prob_p = ifelse(p_grid<0.5, 0, 2)
prob_data = dbinom(6, size=9, prob=p_grid)
posterior = prob_data*prob_p
posterior = posterior/sum(posterior)
```

```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```


## 3M2

```{r}
set.seed(100)
n_samples = 1e4
samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
HPDI(samples, .90)
```

```{r}
post_predictions = rbinom(10000, size=15, prob=samples)
sum(post_predictions == 8)/length(post_predictions)
mean(post_predictions == 8)
```
```{r}
data(homeworkch3)
```

# 3H1

```{r}
set.seed(100)
p_grid = seq(from=0, to=1, length.out=1000)
prior = rep(1, 1000)
total_n_samples = length(birth1)+length(birth2)
total_boys = sum(birth1)+sum(birth2)
likelihood = dbinom(total_boys, size=total_n_samples, prob=p_grid)
posterior = prior*likelihood
posterior = posterior/sum(posterior)
# n_samples = 1e4
# samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
```

```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```

The parameter value that maximises the posterior prob.
```{r}
p_grid[which.max(posterior)]
```

## 3H2

```{r}
n_samples = 1e4
post_samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
```

```{r}
dens(post_samples)
```


```{r}
HPDI(post_samples, .5)
HPDI(post_samples, .89)
HPDI(post_samples, .97)
```
```{r}
# PPD stands for posterior predictive distribution
ppd_samples = rbinom(n_samples, size=200, prob=post_samples) 
```
```{r}
dens(ppd_samples)
```

Yes, the model fits the data well, as the observed value of 111 boys out of 200 births is a central, likely outcome in the empirical distribution of the posterio predictive distribution.

## 3H4

``` {r}
set.seed(100)
p_grid = seq(from=0, to=1, length.out=1000)
prior = rep(1, 1000)
n_samples_b1 = length(birth1)
total_boys_b1 = sum(birth1)
likelihood = dbinom(total_boys_b1, size=n_samples_b1, prob=p_grid)
posterior = prior*likelihood
posterior = posterior/sum(posterior)
# n_samples = 1e4
# samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
```


```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```
The posterior probability distribution for the probability of males is centered close around .5, while considenring both the 1st and 2nd birth it was more shifted more toward 1 (to the right).


## 3H5

``` {r}
set.seed(100)
p_grid = seq(from=0, to=1, length.out=1000)
prior = rep(1, 1000)
n_samples = sum(birth1==0)
n_boys_b2_after_girl_b1 = sum(birth2[birth1==0])
likelihood = dbinom(n_boys_b2_after_girl_b1, size=n_samples, prob=p_grid)
posterior = prior*likelihood
posterior = posterior/sum(posterior)
# n_samples = 1e4
# samples = sample(p_grid, prob=posterior, size=n_samples, replace=T)
```


```{r}
plot(p_grid, posterior, main='Posterior prob. (grid approximate)')
```
