```{r}
library(rethinking)
```

Load the data

```{r}
data(Howell1)
d = Howell1
```

Get some quick info on the variables distribution

```{r}
precis(d)
```
Filter the data of interest (adhults only)
```{r}
d2 = d[d$age>=18,]
```

Make a simple model of the height variable, usign quadratic (Gaussian) approximation for the posteriors. 

```{r}
m4.1 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu ~ dnorm(178, 20), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2) # Observations

```

Display the parameters for the quadratic (Gaussian) approximation for each of the posterions (mu and sigma).
The parameters are the columns mean and sd. Also display a 89% CI for each posterior.

```{r}
precis(m4.1)
```
Display the variance-covariance for the posterior. Along with the parameters above, it provides full information on the posterior obtained with quadratic approximation.
```{r}
vcov(m4.1)
```

From the variance-covariance, extract the vector of variances for the parameters and the correlation matrix

```{r}
diag(vcov(m4.1)) # Same as the square of the `sd` column in the output of precis()
cov2cor(vcov(m4.1))
```

Make the same model, but provide a starting point for the iterative optimization process of the quadratic approximation

```{r}
start = list(mu = mean(d2$height), sigma = sd(d2$height))
m4.1 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu ~ dnorm(178, 20), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2, # Observations
            start = start) # Starting point
```

Extract a random sample from the posterior (note: the posterior is multivariate)

```{r}
post = extract.samples(m4.1, n=100)
head(post)
```
Make a scatterplot of the samples

```{r}
plot(post)
```

A linear model of height as function of weight


```{r}
xbar = mean(d2$weight)
m4.3 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu <- a + b*(weight-xbar), # Linear model
                  a ~ dnorm(178, 20), # Prior
                  b ~ dlnorm(0, 1), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2) # Observations

```

Summarize the marginal distributions of the parameters

```{r}
precis(m4.3)
```
Display the variance-covariance matrix for the fitted quadratic model

```{r}
round(vcov(m4.3),3)
```

