```{r}
library(rethinking)
```

Load the data

```{r}
data(Howell1)
d = Howell1
```

Get some quick info on the variables distribution

```{r}
precis(d)
```
Filter the data of interest (adhults only)
```{r}
d2 = d[d$age>=18,]
```

Make a simple model of the height variable, usign quadratic (Gaussian) approximation for the posteriors. 

```{r}
m4.1 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu ~ dnorm(178, 20), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2) # Observations

```

Display the parameters for the quadratic (Gaussian) approximation for each of the posterions (mu and sigma).
The parameters are the columns mean and sd. Also display a 89% CI for each posterior.

```{r}
precis(m4.1)
```
Display the variance-covariance for the posterior. Along with the parameters above, it provides full information on the posterior obtained with quadratic approximation.
```{r}
vcov(m4.1)
```

From the variance-covariance, extract the vector of variances for the parameters and the correlation matrix

```{r}
diag(vcov(m4.1)) # Same as the square of the `sd` column in the output of precis()
cov2cor(vcov(m4.1))
```

Make the same model, but provide a starting point for the iterative optimization process of the quadratic approximation

```{r}
start = list(mu = mean(d2$height), sigma = sd(d2$height))
m4.1 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu ~ dnorm(178, 20), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2, # Observations
            start = start) # Starting point
```

Extract a random sample from the posterior (note: the posterior is multivariate)

```{r}
post = extract.samples(m4.1, n=100)
head(post)
```
Make a scatterplot of the samples

```{r}
plot(post)
```

A linear model of height as function of weight


```{r}
xbar = mean(d2$weight)
m4.3 = quap(alist(height ~ dnorm(mu, sigma), # Likelihood
                  mu <- a + b*(weight-xbar), # Linear model
                  a ~ dnorm(178, 20), # Prior
                  b ~ dlnorm(0, 1), # Prior
                  sigma ~ dunif(0, 50)), # Prior
            data = d2) # Observations

```

Summarize the marginal distributions of the parameters

```{r}
precis(m4.3)
```
Display the variance-covariance matrix for the fitted quadratic model

```{r}
round(vcov(m4.3),3)
```

Sample from the posterior and take the average of sampled alpha and beta to draw the implied line, over the scatterplot of the data.

```{r}
plot(height ~ weight, data=d2, col=rangi2)
post = extract.samples(m4.3)
a_map = mean(post$a)
b_map = mean(post$b)
curve(a_map + b_map*(x-xbar), add=T)
```

Do it again, but now also add a bundle of lines corresponding to values of mu (the linear relationship)

```{r}
n=100 # How many lines in the bundle

plot(height ~ weight, data=d2, col=rangi2)
post = extract.samples(m4.3)
a_map = mean(post$a)
b_map = mean(post$b)
for (i in 1:n)
  curve(post$a[i] + post$b[i]*(x-xbar), col = col.alpha('black', 0.3), add=T)

curve(a_map + b_map*(x-xbar), col=col.alpha('red', 1), add=T)
```

Make a scatteroplot of the data and overlay the "mean" regression line (MAP line?), a PI of the "mean" regression line and a PI of the simulated data (simulated from the posterior and the likelihood)

```{r}
# Chose the X points for which to overlay the additional informtion
weight.seq = seq(from = 25, to = 70, by = 1) # 46 items

# Take 1000 samples of mu at every X (weight) value in weight.seq
mu = link(m4.3, data=data.frame(weight=weight.seq))
dim(mu)
```
```{r}
# Take the mean of mu by columns, this will be the "mean" regression line (note, it is not exactly the same
# as the one obtained by averaging samples of alpha and samples of beta).
mu.mean = apply(mu, 2, mean)
# Take the 89% percentile intervals (PI) for mu at every point in weight.seq
mu.PI = apply(mu, 2, PI, prob=0.89)
```

```{r}
# Take 1000 simulated heights for every weight value in weight.seq. Each simulated height is sampled
# from a normal distribution with mean mu and std. dev. sigma, where mu is simulated from samples of
# the posterior of alpha and beta, and sigma is sampled from the posterior of sigma.
sim.height = sim(m4.3, data=list(weight=weight.seq))
dim(sim.height)
```

```{r}
# For every weight in weight.seq, compute an 89% percentile interval (PI) of simulated values for the height
height.PI = apply(sim.height, 2, PI, prob=0.89)
```

```{r}
# Plot the data
plot(height ~ weight, d2, col=col.alpha(rangi2,0.5))

# Draw the MAP line
lines(weight.seq, mu.mean)

# Draw the 89% PI region for the MAP line
shade(mu.PI, weight.seq)

# Draw the 89% PI region for the simulated heights
shade(height.PI, weight.seq)
```

